---
title: "v4.OPEX_Forecast.Rolling.Stock.Focus"
author: "Jason Marshall"
date: "September 7, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libs, include=FALSE, echo=FALSE, include = FALSE}
library(forecast) #time series forecast
library(tidyquant)
library(timetk) #edit time serices objects
library(sweep) #tidy model outputs
library(tidyverse) #tidy data
library(broom) #tidy ts model outputs
library(timeDate) #edit ts objects
library(reshape2) #shape data
library(data.table) #shape data setDT
library(readr) #data inport
library(corrr)      # Tidy correlation tables and correlation plotting
library(cowplot)    # Multiple plots with plot_grid()
library(tseries) #adf.test
library(astsa) #lag plot
library(TSA)
#library(DataExplorer) #exploratory data analysis
#library(Hmisc)
#library(caret) #model building
library(quantreg) #quantile regression
library(GGally)
```

```{r load expense data and create wide version of data, echo=FALSE}
####################################################################################
expense.dataset <- read_csv("Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Data/rolling.stock.focus/US.Rolling.Stock.Expense.csv", 
    col_types = cols(Amount = col_number()))

# make unique col names
 colsNamesShelf <-colnames(expense.dataset)
 dataset_col_names <- make.names(colsNamesShelf, unique = TRUE)
 colnames(expense.dataset) <- dataset_col_names

#add date column
 expense.dataset <- expense.dataset %>%
   #add day 01 just to get a complete date
   mutate(day.holder = 01) %>%
   #add year and month
   mutate(date.holder = paste(Year, Acct.Per, day.holder, sep = "-"))

#set date.holder as date
 expense.dataset$date.holder <- as.Date(expense.dataset$date.holder)

# #get last day of the month
 expense.dataset$Date <- as.Date(timeDate::timeLastDayInMonth(expense.dataset$date.holder))

#Filter closed, wholesale, terminal, DC divisions
expense.dataset <- expense.dataset %>% 
  filter(str_detect(Division, "Admin") == FALSE) %>% 
  filter(str_detect(Division, "Closed") == FALSE) %>%
  filter(str_detect(Division, "DC") == FALSE) %>%
  filter(str_detect(Division, "Distribution") == FALSE) %>%
  filter(str_detect(Division, "Wholesale") == FALSE) %>%
  filter(str_detect(Division, "Terminals") == FALSE) %>%
  filter(str_detect(Division, "Terminal") == FALSE)

#create summarized wide dataset
#change strings to factors
#colnames(expense.dataset)
expense.dataset.wide <- expense.dataset %>% mutate_if(is.character, as.factor) %>%
  dplyr::select(Account, Region, Amount, Date) %>%
  group_by(Account, Region,Date) %>%
  summarise(Amount = sum(Amount))

#continue create wide version of data 
expense.dataset.wide <- dcast(data.table::setDT(expense.dataset.wide), 
                                     formula = Date + Region ~ Account,
                                     value.var = c("Amount"),
                                     fun.aggregate = sum)

#create variable: sum(Delivery/plan and field equip)
expense.dataset.wide <- expense.dataset.wide %>%
  mutate(combo.plant.field = `538004 - R&M Delivery Plant Vehicles` + 
           `538006 - R&M Field Equipment`)

#make unique col names
colsNamesShelf <-colnames(expense.dataset.wide)
dataset_col_names <- make.names(colsNamesShelf, unique = TRUE)
colnames(expense.dataset.wide) <- dataset_col_names
#colnames(expense.dataset.wide)

#make total rollstock cols
expense.dataset.wide <- expense.dataset.wide %>%
  mutate(Rolling.Stock =  X538000...Fuel.Petrol + 
           X538004...R.M.Delivery.Plant.Vehicles + 
           X538006...R.M.Field.Equipment + 
           X538007...R.M.Passenger.Vehicles)
#fill NAs
#expense.dataset.wide$Amount <- replace_na(expense.dataset.wide$Amount, 0)

#summary check
#expense.dataset %>% group_by(Region) %>% summarise(sum = sum(Amount))
#summary(expense.dataset.wide)

#test data set
sum(expense.dataset$Amount) == sum(expense.dataset.wide[,3:6])
```


```{r add sales data, echo=FALSE}
US.Sales.Data <- read_csv("Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Data/US_Region_Division_Added_Only_NA_Item_Sales_chopdown_test a557ef9eb.csv")

# #make unique col names
colsNamesShelf <-colnames(US.Sales.Data)
dataset_col_names <- make.names(colsNamesShelf, unique = TRUE)
colnames(US.Sales.Data) <- dataset_col_names

#edit date format 
US.Sales.Data$Invoice.Date <- as.Date(US.Sales.Data$Invoice.Date, format = '%B %d, %Y')

#change invoice date to last month of the year for monthly sum and join with expense data
US.Sales.Data$Invoice.Date <- timeLastDayInMonth(US.Sales.Data$Invoice.Date) 

#change to character to facilitate group_by below
US.Sales.Data$Invoice.Date <- as.character(US.Sales.Data$Invoice.Date)

#summarise by region
US.Sales.Data <- US.Sales.Data %>% select(Invoice.Date, Region, GL.Shelf, Net.Sales)

#create wide version
US.Sales.Data.Wide <- dcast.data.table(data.table::setDT(US.Sales.Data),formula = Invoice.Date + Region ~ GL.Shelf,
                   value.var = c("Net.Sales"),
                   fun.aggregate = sum)

#create total sales col
US.Sales.Data.Wide <- US.Sales.Data.Wide %>%
  mutate(Total.Sales = (APPL + CHEM + FERT + OTHE + SEED))
```

```{r join data sets, echo=FALSE}
#set region to uppper case
expense.dataset.wide$Region <- toupper(expense.dataset.wide$Region)

#replace space in REGION with .
expense.dataset.wide$Region <- gsub(" ", ".", expense.dataset.wide$Region)
US.Sales.Data.Wide$Region <- gsub(" ", ".", US.Sales.Data.Wide$Region)

#create Keys expense data
expense.dataset.wide$key <- paste(expense.dataset.wide$Date, expense.dataset.wide$Region)
expense.dataset.wide$key <- gsub(" ", ".", expense.dataset.wide$key)

#create keys sales data
US.Sales.Data.Wide$key <- paste(US.Sales.Data.Wide$Invoice.Date, US.Sales.Data.Wide$Region)
#fill space between date and region with "."
US.Sales.Data.Wide$key <- gsub(" ", ".", US.Sales.Data.Wide$key)
#join data sets
US.Sales.RollStock.Data <- dplyr::inner_join(x = expense.dataset.wide, y = US.Sales.Data.Wide,
                                             by = "key")

#set Region to factor
US.Sales.RollStock.Data$Region.x <- as.factor(US.Sales.RollStock.Data$Region.x)

#summary(US.Sales.RollStock.Data)
#colnames(US.Sales.RollStock.Data)
```

##Create Nested Datasets By Region
```{r nest data rolling stock by region, echo = FALSE}
#consolidate each dataset by group
Nest.US.Sales.RollStock.Data <- US.Sales.RollStock.Data %>%
  group_by(Region.x) %>%
  nest(.key = "ALL.DATA.TBL")

Nest.US.Sales.RollStock.Data$ALL.DATA.TBL[[1]]

#access each dataset
# Nest.US.Sales.RollStock.Data$data.tbl[[1]][,1:2]
# test <- Nest.US.Sales.RollStock.Data %>% 
#   mutate(fuel.petrol = map(.x = data.tbl, ~US.Sales.RollStock.Data),
#     fuel.petrol = map(data.tbl, ~select(.x, "Date", "X538000...Fuel.Petrol")))
```

```{r create nested objects for each GL group, echo=FALSE}
#colnames(US.Sales.RollStock.Data)
Nest.US.Sales.RollStock.Data <- Nest.US.Sales.RollStock.Data %>%
  #create new nested list for fuel/petrol only
  mutate(FUEL.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                 "Date", 
                                                 "X538000...Fuel.Petrol"))) %>%
  #create new nested list for Delivery Vehix
  mutate(RM.DELIVERY.VEHIX.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                    "Date", 
                                                    "X538004...R.M.Delivery.Plant.Vehicles"))) %>%
  #create new nested list for Field Equip
  mutate(RM.FIELD.EQUIP.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                    "Date", 
                                                    "X538006...R.M.Field.Equipment"))) %>%
  #create new nested list for Field Equip
  mutate(COMBO.PLANT.FIELD.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                    "Date", 
                                                    "combo.plant.field"))) %>%
  #create new nested list for Rolling Stock Total
  mutate(ROLL.STOCK.TOTAL.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                         "Date", 
                                                         "Rolling.Stock"))) %>%
  #create new nested list for total net sales
  mutate(TOTAL.SALES.TBL = map(ALL.DATA.TBL, ~select(.x,
                                                          "Date",
                                                          "Total.Sales")))
Nest.US.Sales.RollStock.Data$FUEL.TBL[[1]][2]
```

```{r COERCE NESTED LISTS TO TS OBJECT, echo = FALSE}
#ADD TIMES SERIES OBJECTS TO NESTED DATASET
TS.Nest.US.Sales.RollStock.Data <- Nest.US.Sales.RollStock.Data %>%
  #create new nested TS list for fuel/petrol only
  mutate(FUEL.TBL.TS = map(
    .x = FUEL.TBL,
    .f = tk_ts,
    start = 2014,
    freq = 12)) %>%
  #create new nested TS list for Delivery Vehix
  mutate(RM.DELIVERY.VEHIX.TBL.TS = map(
    .x = RM.DELIVERY.VEHIX.TBL,
    .f = tk_ts,
    start = 2014,
    freq = 12)) %>%
  #create new nested TS list for Delivery Vehix
  mutate(RM.FIELD.EQUIP.TBL.TS = map(
    .x = RM.FIELD.EQUIP.TBL,
    .f = tk_ts,
    start = 2014,
    freq = 12)) %>%
  #create new nested TS list for combo RM plant field 
  mutate(COMBO.PLANT.FIELD.TBL.TS = map(
    .x = COMBO.PLANT.FIELD.TBL,
    .f = tk_ts,
    start = 2014,
    freq = 12)) %>%
  #create new nested TS list for Rolling Stock Total
  mutate(ROLL.STOCK.TOTAL.TBL.TS = map(
    .x = ROLL.STOCK.TOTAL.TBL,
    .f = tk_ts,
    start = 2014,
    freq = 12)) %>%
  mutate(TOTAL.SALES.TBL.TS = map(
    .x = ROLL.STOCK.TOTAL.TBL,
    .f = tk_ts,
    freq = 12))

TS.Nest.US.Sales.RollStock.Data
```
#Plot TS Data
```{r PLOT EACH  fuel TS OBJECT, echo=FALSE}
#plot fuel data vs sales
for (i in 1:6) {
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- autoplot(TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS[[i]]) +
  geom_smooth(method = 'loess') +
  ggtitle(paste("Fuel", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}
```

```{r PLOT EACH RM Delivery Vehicle OBJECT, echo=FALSE}
#plot RM Field 
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- autoplot(TS.Nest.US.Sales.RollStock.Data$RM.DELIVERY.VEHIX.TBL.TS[[i]]) +
  geom_smooth(method = 'loess') + 
  ggtitle(paste("Delivery Vehicle", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

```{r PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- autoplot(TS.Nest.US.Sales.RollStock.Data$RM.FIELD.EQUIP.TBL.TS[[i]]) + 
  geom_smooth(method = 'loess') +
  ggtitle(paste("RM Field Equip", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

```{r PLOT EACH combo.plant.field, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- autoplot(TS.Nest.US.Sales.RollStock.Data$COMBO.PLANT.FIELD.TBL.TS[[i]]) +
  geom_smooth(method = 'loess') +
  ggtitle(paste("COMBO.PLANT.FIELD", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

```{r PLOT EACH Rolling Stock OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- autoplot(TS.Nest.US.Sales.RollStock.Data$ROLL.STOCK.TOTAL.TBL.TS[[i]]) +
  geom_smooth(method = 'loess') +
  ggtitle(paste("Rolling Stock Total", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

```{r PLOT EACH total sales OBJECT, echo=FALSE}
#plot total sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- autoplot(TS.Nest.US.Sales.RollStock.Data$TOTAL.SALES.TBL.TS [[i]]) +
  geom_smooth(method = 'loess') +
  ggtitle(paste("Net Sales Total", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

#ACF of each variable
```{r ACF PLOT EACH  fuel TS OBJECT, echo=FALSE}
#plot fuel data vs sales
for (i in 1:6) {
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggAcf(TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS[[i]]) + 
  ggtitle(paste("ACF Plot Fuel", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}
```
## Commentary 
# Seasonal autocorrelation at lag 12 for all Regions
```{r ACF PLOT EACH RM Delivery Vehicle OBJECT, echo=FALSE}
#plot RM Field 
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggAcf(TS.Nest.US.Sales.RollStock.Data$RM.DELIVERY.VEHIX.TBL.TS[[i]]) + ggtitle(paste("ACF Plot Delivery Vehicle", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```
##Commentary 
#Central Cornbelt: Sig autocorrelation at lag 1, light seasonal autocorr at lag 12
#Eastern: Sig autocorr at lag 1, light seasonal autocorr at lag 12
#ECB: Sig autocorr at lag 1, sig seasonal autocorr at lag 12
#South: Sig autocorr at lag 1, no sig seasonal autocorr at lag 12, sig negative auto.corr at lag 18
#West: Sig autocorr at lag 1, no sig autocorr at lag 12, light neg autocorr at 16/18.
#Western.Cornbelt: Sig autocorr at lag 1, no sig autocorr at lag 12. sig neg autocorr at lag 15.

```{r ACF PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggAcf(TS.Nest.US.Sales.RollStock.Data$RM.FIELD.EQUIP.TBL.TS[[i]]) + 
  ggtitle(paste("ACF Plot RM Field Equip", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

##Commentary
#CCB: Sig autocorr at lag 1, no seasonal autocorr
#Eastern: sig autocorr at lag 1, no seasonal autocorr
#ECB: Sig autocorr at lag 1, light seasonal autocorr
#South: Sig autocorr at lag 1, marginal seasonal autocorr
#West: Sig autocorr at lag 1, no seasonal autocorr
#WCB: Sig autocorr at lag 1, Sig seasonal autocorr

```{r ACF PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggAcf(TS.Nest.US.Sales.RollStock.Data$COMBO.PLANT.FIELD.TBL.TS[[i]]) + 
  ggtitle(paste("ACF Plot COMBO PLANT and FIELD", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

##Commentary
#CCB: moderate autocorr at lag 1, sig seasonal autocorr
#Eastern: sig autocorr at lag 1, sig seasonal autocorr
#ECB: Sig autocorr at lag 1, Sig seasonal autocorr
#South: Sig autocorr at lag 1, SIG seasonal autocorr
#West: Sig autocorr at lag 1, SIG seasonal autocorr
#WCB: Sig autocorr at lag 1, Sig seasonal autocorr

```{r ACF PLOT EACH Rolling Stock OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggAcf(TS.Nest.US.Sales.RollStock.Data$ROLL.STOCK.TOTAL.TBL.TS[[i]]) + ggtitle(paste("ACF Plot Rolling Stock Total", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

##Commentary
#CCB: moderate autocorr at lag 1, sig seasonal autocorr @ lag 12
#Eastern: sig autocorr at lag 1, sig seasonal autocorr @ lag 12
#ECB: Sig autocorr at lag 1, Sig seasonal autocorr @ lag 12
#South: Sig autocorr at lag 1, SIG seasonal autocorr @ lag 12
#West: Sig autocorr at lag 1, SIG seasonal autocorr @ lag 12
#WCB: Sig autocorr at lag 1, Sig seasonal autocorr @ lag 12

```{r ACF PLOT EACH  sales TS OBJECT, echo=FALSE}
#plot fuel data vs sales
for (i in 1:6) {
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggAcf(TS.Nest.US.Sales.RollStock.Data$TOTAL.SALES.TBL.TS[[i]]) + 
  ggtitle(paste("ACF Net.Sales", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}
```

#PACF of each variable
```{r ACF PLOT EACH  fuel TS OBJECT, echo=FALSE}
#plot fuel data vs sales
for (i in 1:6) {
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggPacf(TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS[[i]]) + 
  ggtitle(paste("PACF Plot Fuel", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}
```
##Commentary
#CCB: sig pac al lag 1 and trails off gradually. possible MA(2) model
#EASTERN: sig pac at 1 and 9 then trails off gradually
#ECB: sig pac at lag 1 and then trails gradually
#South: sig pac at lag 1 and then trails off gradually
#West: sig pac at lag 1 
#WCB: sig pac at lag 1... then trails off gradually

```{r PACF PLOT EACH RM Delivery Vehicle OBJECT, echo=FALSE}
#plot RM Field 
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggPacf(TS.Nest.US.Sales.RollStock.Data$RM.DELIVERY.VEHIX.TBL.TS[[i]]) + ggtitle(paste("PACF Plot Delivery Vehicle", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

```{r PACF PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggPacf(TS.Nest.US.Sales.RollStock.Data$RM.FIELD.EQUIP.TBL.TS[[i]]) + 
  ggtitle(paste("PACF Plot RM Field Equip", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

```{r PACF PLOT EACH Rolling Stock OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggPacf(TS.Nest.US.Sales.RollStock.Data$COMBO.PLANT.FIELD.TBL.TS[[i]]) + 
  ggtitle(paste("PACF Plot Combo Plant/Field", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
```

```{r PACF PLOT EACH Rolling Stock OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggPacf(TS.Nest.US.Sales.RollStock.Data$ROLL.STOCK.TOTAL.TBL.TS[[i]]) + ggtitle(paste("PACF Plot Rolling Stock Total", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
```

```{r ACF PLOT EACH  fuel TS OBJECT, echo=FALSE}
#plot fuel data vs sales
for (i in 1:6) {
region.name <- TS.Nest.US.Sales.RollStock.Data$Region.x[[i]]
ts.plot <- ggPacf(TS.Nest.US.Sales.RollStock.Data$TOTAL.SALES.TBL.TS[[i]]) + 
  ggtitle(paste("PACF Plot Net Sales", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}
```


#fit models
```{r Fit Models, echo=FALSE}
# model.name <- "fuel.petrol.fit"
# TS.OBJECT <- TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
# X.Reg <- TS.Nest.US.Sales.RollStock.Data$TOTAL.SALES.TBL
# new.var.name.1 <- "ETS.FIT"
# new.var.name.2 <- "ARIMA.FIT"
# augment.var.1 <- 
# augment.var.2 <- 
# 
# 
# #fit model
# model.name <- TS.Nest.US.Sales.RollStock.Data %>%
#   mutate(new.var.name.1 = map(TS.OBJECT, ets),
#                        new.var.name.2 = map(TS.OBJECT, auto.arima, xreg = TS.Nest.US.Sales.RollStock.Data$TOTAL.SALES.TBL.TS))
# 
# #model parameters
# #ETS
# model.params.1 <- model.name %>%
#   mutate(tidy = map(new.var.name.1, sw_glance)) %>%
#   unnest(tidy, .drop=TRUE) 
# #ARIMA
# model.params.2 <- model.name %>%
#   mutate(tidy = map(new.var.name.2, sw_glance)) %>%
#   unnest(tidy, .drop=TRUE)
# 
# #plot models
# fuel.augment.ets <- fuel.petrol.fit %>%
#   mutate(augment = map(ETS.FIT, sw_augment, timetk_idx = TRUE, rename_index = "Date")) %>%
#   unnest(augment)
# 
# fuel.augment.ets %>%
#     ggplot(aes(x = Date, y = .resid, group = Region.x)) +
#     geom_hline(yintercept = 0, color = "grey40") +
#     geom_line(color = palette_light()[[2]]) +
#     geom_smooth(method = "loess") +
#     labs(title = "Fuel/Petrol by Region",
#          subtitle = "ETS Model Residuals", x = "") + 
#     theme_tq() +
#     facet_wrap(~ Region.x, scale = "free_y", ncol = 3) +
#     scale_x_date(date_labels = "%Y") 
```

##ETS Function

``````{r ETS forecast function, echo=FALSE}
ETS_Func <- function(nested.dataset, colName, 
                     Res.Plot.Title = "Insert.Plot.Title", 
                     fcast.plot.title = "Insert Plot Title"){
  #test vars
  # nested.dataset <- TS.Nest.US.Sales.RollStock.Data
  # colName <- TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
  # Res.Plot.Title <- "Insert.Plot.Title"
  # fcast.plot.title <- "Insert Plot Title"
  #fit model
  model.fit <- nested.dataset %>%
    mutate(new.col.model.name = map(colName, ets))
  
  #forecast model
  fcast.model.fit <- model.fit %>%
    mutate(fcast.model = map(new.col.model.name, forecast, h = 12))
  
  #model parameters
  #ETS
  model.params <- model.fit %>%
    mutate(tidy = map(new.col.model.name, sw_glance)) %>%
    unnest(tidy, .drop=TRUE)%>% 
    select(Region.x, model.desc, AIC, BIC, RMSE, MAPE)

  #get tidy model residuals
  augment.data <- model.fit %>%
    mutate(augment.var = map(new.col.model.name, 
                         sw_augment, 
                         timetk_idx = TRUE, 
                         rename_index = "Date")) %>%
    unnest(augment.var, .drop = TRUE) 
  
  #plot model residuals 
  data.plot.residuals <- augment.data %>%
    ggplot(aes(x = Date, y = .resid, group = Region.x)) +
    geom_hline(yintercept = 0, color = "grey40") +
    geom_line(color = palette_light()[[2]]) +
    geom_smooth(method = "loess") +
    labs(title = Res.Plot.Title,
         subtitle = "ETS Model Residuals", x = "") +
    theme_tq() +
    facet_wrap(~ Region.x, scale = "free_y", ncol = 3) +
    scale_x_date(date_labels = "%Y")
  
  #get tidy forecast data
  fcast.model.fit.tidy <- fcast.model.fit %>%
    mutate(sweep = map(fcast.model, 
                       sw_sweep, 
                       fitted = TRUE,
                       timetk_idx = TRUE)) %>%
    unnest(sweep)
  
  #plot fcast
  data.plot.fcast <- fcast.model.fit.tidy %>%
    ggplot(mapping = aes_string(x =  names(fcast.model.fit.tidy)[2], 
                      y = names(fcast.model.fit.tidy)[4], 
                      color = names(fcast.model.fit.tidy)[3], 
                      group = names(fcast.model.fit.tidy)[1])) + 
    geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
                fill = "#D5DBFF", color = NA, size = 0) +
    geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
                fill = "#596DD5", color = NA, size = 0, alpha = 0.8) +
    geom_line() +
    labs(title = fcast.plot.title,
         subtitle = "ETS Model Forecasts",
         x = "", y = "Units") +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
    scale_color_tq() +
    scale_fill_tq() +
    facet_wrap(~ Region.x, scales = "free_y", ncol = 2) +
    theme_tq() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  #return.list <- list(model.params, data.plot.residuals, fcast.model.fit.tidy, data.plot.fcast)
  return(fcast.model.fit.tidy)
}

##ARIMA Function
```{r ARIMA forecast function, echo=FALSE}
AUTO.ARIMA_Func <- function(nested.dataset, colName, 
                     Res.Plot.Title = "Insert.Plot.Title", 
                     fcast.plot.title = "Insert Plot Title"){
  #test vars
  # nested.dataset <- TS.Nest.US.Sales.RollStock.Data
  # colName <- TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
  # Res.Plot.Title <- "Insert.Plot.Title"
  # fcast.plot.title <- "Insert Plot Title"
  #fit model
  model.fit <- nested.dataset %>%
    mutate(new.col.model.name = map(colName, auto.arima))
  
  #forecast model
  fcast.model.fit <- model.fit %>%
    mutate(fcast.model = map(new.col.model.name, forecast, h = 12))
  
  #model parameters
  #ARIMA
  model.params <- model.fit %>%
    mutate(tidy = map(new.col.model.name, sw_glance)) %>%
    unnest(tidy, .drop=TRUE) %>%
    select(Region.x, model.desc, AIC, BIC, RMSE, MAPE)

  #get tidy model residuals
  augment.data <- model.fit %>%
    mutate(augment.var = map(new.col.model.name, 
                         sw_augment, 
                         timetk_idx = TRUE, 
                         rename_index = "Date")) %>%
    unnest(augment.var, .drop = TRUE)
  
  #plot model residuals 
  data.plot.residuals <- augment.data %>%
    ggplot(aes(x = Date, y = .resid, group = Region.x)) +
    geom_hline(yintercept = 0, color = "grey40") +
    geom_line(color = palette_light()[[2]]) +
    geom_smooth(method = "loess") +
    labs(title = Res.Plot.Title,
         subtitle = "ARIMA Model Residuals", x = "") +
    theme_tq() +
    facet_wrap(~ Region.x, scale = "free_y", ncol = 2) +
    scale_x_date(date_labels = "%Y")
  
  #get tidy forecast data
  fcast.model.fit.tidy <- fcast.model.fit %>%
    mutate(sweep = map(fcast.model, 
                       sw_sweep, 
                       fitted = TRUE,
                       timetk_idx = TRUE)) %>% 
    unnest(sweep)
  
  #plot fcast
  data.plot.fcast <- fcast.model.fit.tidy %>%
    ggplot(mapping = aes_string(x =  names(fcast.model.fit.tidy)[2], 
                      y = names(fcast.model.fit.tidy)[4], 
                      color = names(fcast.model.fit.tidy)[3], 
                      group = names(fcast.model.fit.tidy)[1])) + 
    geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
                fill = "#D5DBFF", color = NA, size = 0) +
    geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
                fill = "#596DD5", color = NA, size = 0, alpha = 0.8) +
    geom_line() +
    labs(title = fcast.plot.title,
         subtitle = "ARIMA Model Forecasts",
         x = "", y = "Units") +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
    scale_color_tq() +
    scale_fill_tq() +
    facet_wrap(~ Region.x, scales = "free_y", ncol = 2) +
    theme_tq() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  #return.list <- list(model.params, data.plot.residuals, fcast.model.fit.tidy, data.plot.fcast)
  return(fcast.model.fit.tidy)
}
```

##TSLM Function
```{r TSLM forecast function, echo=FALSE}
# TSLM_Func <- function(nested.dataset, colName, 
#                      Res.Plot.Title = "Insert.Plot.Title", 
#                      fcast.plot.title = "Insert Plot Title"){
#   #test vars
#   # nested.dataset <- TS.Nest.US.Sales.RollStock.Data
#   # colName <- TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
#   # Res.Plot.Title <- "Insert.Plot.Title"
#   # fcast.plot.title <- "Insert Plot Title"
#   
#   #fit TSLM odel
#   model.fit <- nested.dataset %>%
#     mutate(new.col.model.name = map(nested.dataset[,colName], ~tslm(.x ~ season + trend)))
#   
#   #forecast model
#   fcast.model.fit <- model.fit %>%
#     mutate(fcast.model = map(new.col.model.name, forecast, h = 12))
#   
#   #model parameters
#   #TSLM
#   model.params <- model.fit %>%
#     mutate(tidy = map(new.col.model.name, sw_glance)) %>%
#     unnest(tidy, .drop=TRUE) 
# 
#   #get tidy model residuals
#   augment.data <- model.fit %>%
#     mutate(augment.var = map(new.col.model.name, 
#                          sw_augment, 
#                          timetk_idx = TRUE, 
#                          rename_index = "Date")) %>%
#     unnest(augment.var, .drop = TRUE)
#   
#   #plot model residuals 
#   data.plot.residuals <- augment.data %>%
#     ggplot(aes(x = Date, y = .resid, group = Region.x)) +
#     geom_hline(yintercept = 0, color = "grey40") +
#     geom_line(color = palette_light()[[2]]) +
#     geom_smooth(method = "loess") +
#     labs(title = Res.Plot.Title,
#          subtitle = "TSLM Model Residuals", x = "") +
#     theme_tq() +
#     facet_wrap(~ Region.x, scale = "free_y", ncol = 2) +
#     scale_x_date(date_labels = "%Y")
#   
#   #get tidy forecast data
#   fcast.model.fit.tidy <- fcast.model.fit %>%
#     mutate(sweep = map(fcast.model, 
#                        sw_sweep, 
#                        fitted = TRUE,
#                        timetk_idx = TRUE)) %>%
#     unnest(sweep)
#   
#   #plot fcast
#   data.plot.fcast <- fcast.model.fit.tidy %>%
#     ggplot(mapping = aes_string(x =  names(fcast.model.fit.tidy)[2], 
#                       y = names(fcast.model.fit.tidy)[4], 
#                       color = names(fcast.model.fit.tidy)[3], 
#                       group = names(fcast.model.fit.tidy)[1])) + 
#     geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
#                 fill = "#D5DBFF", color = NA, size = 0) +
#     geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
#                 fill = "#596DD5", color = NA, size = 0, alpha = 0.8) +
#     geom_line() +
#     labs(title = fcast.plot.title,
#          subtitle = "TSLM Model Forecasts",
#          x = "", y = "Units") +
#     scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
#     scale_color_tq() +
#     scale_fill_tq() +
#     facet_wrap(~ Region.x, scales = "free_y", ncol = 2) +
#     theme_tq() +
#     theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
#   return.list <- list(model.params, data.plot.residuals, data.plot.fcast)
#   return(return.list)
# }
```

##Fuel Expense Forecast
```{r Fuel Expense Models, echo = FALSE}
#ETS Forecast Model
ets.forecast <- ETS_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS, 
         "Fuel Expense", "Fuel Expense")

#ARIMA Forecast Model
arima.forecast <- AUTO.ARIMA_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS, 
         "Fuel Expense", "Fuel Expense")

#Create and combine forecast dataframes 
a <- ets.forecast %>%
  mutate(variable = rep(names(ets.forecast[4]))) %>%
  mutate(Model = rep("ETS"))

colnames(a)[4] <- c("Amount")

b <- arima.forecast %>%
  mutate(variable = rep(names(arima.forecast[4])))%>%
  mutate(Model = rep("ARIMA"))

colnames(b)[4] <- c("Amount")
```

##Delivery Vehicle
```{r Fuel Expense Models, echo = FALSE}
#ETS Forecast Model
ets.forecast <- ETS_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$RM.DELIVERY.VEHIX.TBL.TS, 
         "Delivery Vehicle", "Delivery Vehicle")

#ARIMA Forecast Model
arima.forecast <- AUTO.ARIMA_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$RM.DELIVERY.VEHIX.TBL.TS, 
         "Delivery Vehicle", "Delivery Vehicle")

#Create and combine forecast dataframes 
c <- ets.forecast %>%
  mutate(variable = rep(names(ets.forecast[4]))) %>%
  mutate(Model = rep("ETS"))

colnames(c)[4] <- c("Amount")

d <- arima.forecast %>%
  mutate(variable = rep(names(arima.forecast[4])))%>%
  mutate(Model = rep("ARIMA"))

colnames(d)[4] <- c("Amount")

```

##Field.Equipment Forecast
```{r Field Equipment, echo = FALSE}
#ETS Forecast Model
ets.forecast <- ETS_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$RM.FIELD.EQUIP.TBL.TS, 
         "Field.Equipment", "Field.Equipment")

#ARIMA Forecast Model
arima.forecast <- AUTO.ARIMA_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$RM.FIELD.EQUIP.TBL.TS, 
         "Field.Equipment", "Field.Equipment")

#Create and combine forecast dataframes 
e <- ets.forecast %>%
  mutate(variable = rep(names(ets.forecast[4]))) %>%
  mutate(Model = rep("ETS"))

colnames(e)[4] <- c("Amount")

f <- arima.forecast %>%
  mutate(variable = rep(names(arima.forecast[4])))%>%
  mutate(Model = rep("ARIMA"))

colnames(f)[4] <- c("Amount")
```

##COMBO.PLANT.FIELD Forecast
```{r COMBO PLANT FIELD, echo = FALSE}
#ETS Forecast Model
ets.forecast <- ETS_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$COMBO.PLANT.FIELD.TBL.TS, 
         "COMBO.PLANT.FIELD", "COMBO.PLANT.FIELD")

#ARIMA Forecast Model
arima.forecast <- AUTO.ARIMA_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$COMBO.PLANT.FIELD.TBL.TS, 
         "COMBO.PLANT.FIELD", "COMBO.PLANT.FIELD")

#Create and combine forecast dataframes 
g <- ets.forecast %>%
  mutate(variable = rep(names(ets.forecast[4]))) %>%
  mutate(Model = rep("ETS"))

colnames(g)[4] <- c("Amount")

h <- arima.forecast %>%
  mutate(variable = rep(names(arima.forecast[4])))%>%
  mutate(Model = rep("ARIMA"))

colnames(h)[4] <- c("Amount")
```

##ROLL.STOCK.TOTAL.TBL.TS Forecast
```{r ROLL STOCK TOTAL TBL TS, echo = FALSE}
#ETS Forecast Model
ets.forecast <- ETS_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$ROLL.STOCK.TOTAL.TBL.TS, 
         "ROLL.STOCK.TOTAL.TBL.TS", "ROLL.STOCK.TOTAL.TBL.TS")

#ARIMA Forecast Model
arima.forecast <- AUTO.ARIMA_Func(TS.Nest.US.Sales.RollStock.Data, TS.Nest.US.Sales.RollStock.Data$ROLL.STOCK.TOTAL.TBL.TS, 
         "ROLL.STOCK.TOTAL.TBL.TS", "ROLL.STOCK.TOTAL.TBL.TS")

#Create and combine forecast dataframes 
i <- ets.forecast %>%
  mutate(variable = rep(names(ets.forecast[4]))) %>%
  mutate(Model = rep("ETS"))

colnames(i)[4] <- c("Amount")

j <- arima.forecast %>%
  mutate(variable = rep(names(arima.forecast[4])))%>%
  mutate(Model = rep("ARIMA"))

colnames(j)[4] <- c("Amount")
```

```{r bind rows, echo=false}
#bind rows
forecast.data <- bind_rows(a,b,c,d,e,f,g,h,i,j)

#write to disk
write.csv(forecast.data,"Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Results/forecast.data.csv")
```














