---
title: "Untitled"
author: "Jason Marshall"
date: "September 13, 2018"
output: word_document
---
#Version 5 code cleanup. 
#write more functions to improve code quality.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libs, include=FALSE, echo=FALSE, include = FALSE}
library(forecast) #time series forecast
library(tidyquant)
library(timetk) #edit time serices objects
library(sweep) #tidy model outputs
library(tidyverse) #tidy data
library(broom) #tidy ts model outputs
library(timeDate) #edit ts objects
library(reshape2) #shape data
library(data.table) #shape data setDT
library(readr) #data inport
library(corrr)      # Tidy correlation tables and correlation plotting
library(cowplot)    # Multiple plots with plot_grid()
library(tseries) #adf.test
library(astsa) #lag plot
library(TSA)
#library(DataExplorer) #exploratory data analysis
#library(Hmisc)
#library(caret) #model building
library(quantreg) #quantile regression
library(GGally)
```

```{r load functions} 
#create R compatible colnames
func.unique.colNames <- function(dataset){
  #1. Load Data
  #2. Data Transforms
  #3. Create a "wide" version of data
  
  #Get colnames
  colsNamesShelf <-colnames(dataset)
  # make unique col names
  dataset_col_names <- make.names(colsNamesShelf, unique = TRUE)
  #set new colnames
  colnames(dataset) <- dataset_col_names
}
#load expense data
func.load.exp <- function(path){
  #load data
  expense.dataset <- read_csv(path, col_types = cols(Amount = col_number()))
  
  #make unique colnames
  colnames(expense.dataset) <- func.unique.colNames(expense.dataset)
  
  #add date column
  expense.dataset <- expense.dataset %>%
    #add day 01 just to get a complete date
    mutate(day.holder = 01) %>%
    #add year and month
    mutate(date.holder = paste(Year, Acct.Per, day.holder, sep = "-"))
  
  #set date.holder as date
  expense.dataset$date.holder <- as.Date(expense.dataset$date.holder)
  
  #get last day of the month
  expense.dataset$Date <- as.Date(timeDate::timeLastDayInMonth(expense.dataset$date.holder))
  
  #Filter closed, wholesale, terminal, DC divisions
  expense.dataset <- expense.dataset %>% 
  filter(str_detect(Division, "Admin") == FALSE) %>% 
  filter(str_detect(Division, "Closed") == FALSE) %>%
  filter(str_detect(Division, "DC") == FALSE) %>%
  filter(str_detect(Division, "Distribution") == FALSE) %>%
  filter(str_detect(Division, "Wholesale") == FALSE) %>%
  filter(str_detect(Division, "Terminals") == FALSE) %>%
  filter(str_detect(Division, "Terminal") == FALSE)

  #create summarized wide dataset
  #select needed variables
  #change strings to factors
  expense.dataset <- expense.dataset %>% mutate_if(is.character, as.factor) %>%
    #select variables
    dplyr::select(Account, Region, Amount, Date) %>%
    #group by account/region/date
    group_by(Account, Region,Date) %>%
    #sum expense amount
    summarise(Amount = sum(Amount))
  
  #continue create wide version of data 
  expense.dataset.wide <- dcast(data.table::setDT(expense.dataset), 
                                     formula = Date + Region ~ Account,
                                     value.var = c("Amount"),
                                     fun.aggregate = sum)
  
  #edit colnames
  colnames(expense.dataset.wide) <- gsub(pattern = " - ", 
                                         replacement = ".", 
                                         x = colnames(expense.dataset.wide))
  #make unique col names
  colnames(expense.dataset.wide) <- func.unique.colNames(expense.dataset.wide)
  
  #create variable: sum(Delivery/plan and field equip)
  expense.dataset.wide <- expense.dataset.wide %>%
    mutate(combo.plant.field = X538004.R.M.Delivery.Plant.Vehicles + 
             X538006.R.M.Field.Equipment)
  
  #make total rollstock cols
  expense.dataset.wide <- expense.dataset.wide %>%
  mutate(Rolling.Stock =  X538000.Fuel.Petrol + 
           X538004.R.M.Delivery.Plant.Vehicles + 
           X538006.R.M.Field.Equipment + 
           X538007.R.M.Passenger.Vehicles)
  
  #return "wide" version of dataset
  return(expense.dataset.wide)
}

#load sales data
func.load.sales <- function(path){
  #load sales data
  US.Sales.Data <- read_csv(path) ###### Delete n_max after testing######
  
  #make uniques col names
  colnames(US.Sales.Data) <- func.unique.colNames(US.Sales.Data)
  
  #edit date format 
  US.Sales.Data$Invoice.Date <- as.Date(US.Sales.Data$Invoice.Date, format = '%B %d, %Y')
  
  #change invoice date to last month of the year for monthly sum and join with expense data
  US.Sales.Data$Invoice.Date <- timeLastDayInMonth(US.Sales.Data$Invoice.Date)
  
  #change to character to facilitate group_by below
  US.Sales.Data$Invoice.Date <- as.character(US.Sales.Data$Invoice.Date)
  
  #summarise by region
  US.Sales.Data <- US.Sales.Data %>% select(Invoice.Date, Region, GL.Shelf, Net.Sales)
  
  #create wide version
  US.Sales.Data.Wide <- dcast.data.table(data.table::setDT(US.Sales.Data),formula = Invoice.Date + Region ~ GL.Shelf,
                   value.var = c("Net.Sales"),
                   fun.aggregate = sum)
  
  #create total sales col
  US.Sales.Data.Wide <- US.Sales.Data.Wide %>%
    mutate(Total.Sales = (APPL + CHEM + FERT + OTHE + SEED))
}

#join sales and expense data
func.join.datasets <- function(sales.dataset, expense.dataset){
  #set region to uppper case
  expense.dataset$Region <- toupper(expense.dataset$Region)
  
  #replace space in REGION with .
  expense.dataset$Region <- gsub(" ", ".", expense.dataset$Region)
  sales.dataset$Region <- gsub(" ", ".", sales.dataset$Region)
  
  #create Keys expense data
  #paste date and region to get data by region by date
  expense.dataset$key <- paste(expense.dataset$Date, expense.dataset$Region)
  #put . in space between region and date
  expense.dataset$key <- gsub(" ", ".", expense.dataset$key)
  
  #create keys sales data
  #paste date and region to get data by region by date
  sales.dataset$key <- paste(sales.dataset$Invoice.Date, sales.dataset$Region)
  #fill space between date and region with "."
  sales.dataset$key <- gsub(" ", ".", sales.dataset$key)
  
  #join data sets
  US.Sales.RollStock.Data <- dplyr::inner_join(x = expense.dataset, y = sales.dataset,
                                             by = "key")
  #set Region to factor
  US.Sales.RollStock.Data$Region.x <- as.factor(US.Sales.RollStock.Data$Region.x)
  
  #return dataset
  return(US.Sales.RollStock.Data)
}

#nest datasets into tibbles
func.nest.data <- function(dataset){
  #consolidate each dataset by group
  nested.dataset <- dataset %>%
  group_by(Region.x) %>%
  nest(.key = "ALL.DATA.TBL")
  
  #colnames(US.Sales.RollStock.Data)
  nested.dataset <- nested.dataset %>%
  #create new nested list for fuel/petrol only
  # mutate(FUEL.TBL = map(ALL.DATA.TBL, ~select(.x, 
  #                                                "Date", 
  #                                                "X538000.Fuel.Petrol",
  #                                             "Total.Sales"))) %>%
  mutate(FUEL.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                               "Date", 
                                               "X538000.Fuel.Petrol",
                                                          "Total.Sales"))) %>%
  #create new nested list for Delivery Vehix
  mutate(RM.DELIVERY.VEHIX.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                    "Date", 
                                                    "X538004.R.M.Delivery.Plant.Vehicles"))) %>%
  #create new nested list for Field Equip
  mutate(RM.FIELD.EQUIP.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                    "Date", 
                                                    "X538006.R.M.Field.Equipment"))) %>%
  #create new nested list for Field Equip
  mutate(COMBO.PLANT.FIELD.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                    "Date", 
                                                    "combo.plant.field"))) %>%
  #create new nested list for Rolling Stock Total
  mutate(ROLL.STOCK.TOTAL.TBL = map(ALL.DATA.TBL, ~select(.x, 
                                                         "Date", 
                                                         "Rolling.Stock"))) %>%
  #create new nested list for total net sales
  mutate(TOTAL.SALES.TBL = map(ALL.DATA.TBL, ~select(.x,
                                                          "Date",
                                                          "Total.Sales")))
  return(nested.dataset)
}

#nest datasets in to TS objects
func.ts.nest.dataset <- function(nested.dataset){
  #ADD TIMES SERIES OBJECTS TO NESTED DATASET
  nested.dataset.TS <- nested.dataset %>%
    #create new nested TS list for fuel/petrol only
    mutate(FUEL.TBL.TS = map(
      .x = FUEL.TBL,
      .f = tk_ts,
      start = 2014,
      freq = 12)) %>%
    #create new nested TS list for Delivery Vehix
    mutate(RM.DELIVERY.VEHIX.TBL.TS = map(
      .x = RM.DELIVERY.VEHIX.TBL,
      .f = tk_ts,
      start = 2014,
      freq = 12)) %>%
    #create new nested TS list for Delivery Vehix
    mutate(RM.FIELD.EQUIP.TBL.TS = map(
      .x = RM.FIELD.EQUIP.TBL,
      .f = tk_ts,
      start = 2014,
      freq = 12)) %>%
    #create new nested TS list for combo RM plant field 
    mutate(COMBO.PLANT.FIELD.TBL.TS = map(
      .x = COMBO.PLANT.FIELD.TBL,
      .f = tk_ts,
      start = 2014,
      freq = 12)) %>%
    #create new nested TS list for Rolling Stock Total
    mutate(ROLL.STOCK.TOTAL.TBL.TS = map(
      .x = ROLL.STOCK.TOTAL.TBL,
      .f = tk_ts,
      start = 2014,
      freq = 12)) %>%
    mutate(TOTAL.SALES.TBL.TS = map(
      .x = ROLL.STOCK.TOTAL.TBL,
      .f = tk_ts,
      freq = 12))
  return(nested.dataset.TS)
}

func.ets.mods <- function(nested.dataset, colName,
                          Exp.Variable,
                          Res.Plot.Title = "Insert.Plot.Title",
                          fcast.plot.title = "Insert Plot Title"){
  #test vars
  # nested.dataset <- TS.Nest.US.Sales.RollStock.Data
  # colName <- TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
  # Res.Plot.Title <- "Insert.Plot.Title"
  # fcast.plot.title <- "Insert Plot Title"
  #fit model
  
  model.fit <- nested.dataset %>%
    mutate(new.col.model.name = map(colName, ets))
  
  #forecast model
  fcast.model.fit <- model.fit %>%
    mutate(fcast.model = map(new.col.model.name, forecast, h = 12))
  
  #model parameters
  #ETS
  model.params <- model.fit %>%
    mutate(tidy = map(new.col.model.name, sw_glance)) %>%
    unnest(tidy, .drop=TRUE)%>%
    mutate(Exp.Variable = rep(Exp.Variable)) %>%
    select(Region.x, model.desc, AIC, BIC, RMSE, MAPE, Exp.Variable)

  #get tidy model residuals
  augment.data <- model.fit %>%
    mutate(augment.var = map(new.col.model.name, 
                         sw_augment, 
                         timetk_idx = TRUE, 
                         rename_index = "Date")) %>%
    unnest(augment.var, .drop = TRUE) 
  
  #plot model residuals 
  data.plot.residuals <- augment.data %>%
    ggplot(aes(x = Date, y = .resid, group = Region.x)) +
    geom_hline(yintercept = 0, color = "grey40") +
    geom_line(color = palette_light()[[2]]) +
    geom_smooth(method = "loess") +
    labs(title = Res.Plot.Title,
         subtitle = "ETS Model Residuals", x = "") +
    theme_tq() +
    facet_wrap(~ Region.x, scale = "free_y", ncol = 3) +
    scale_x_date(date_labels = "%Y")
  
  #get tidy forecast data
  fcast.model.fit.tidy <- fcast.model.fit %>%
    mutate(sweep = map(fcast.model, 
                       sw_sweep, 
                       fitted = TRUE,
                       timetk_idx = TRUE)) %>%
    unnest(sweep)
  
  #plot fcast
  data.plot.fcast <- fcast.model.fit.tidy %>%
    ggplot(mapping = aes_string(x =  names(fcast.model.fit.tidy)[2], 
                      y = names(fcast.model.fit.tidy)[4], 
                      color = names(fcast.model.fit.tidy)[3], 
                      group = names(fcast.model.fit.tidy)[1])) + 
    geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
                fill = "#D5DBFF", color = NA, size = 0) +
    geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
                fill = "#596DD5", color = NA, size = 0, alpha = 0.8) +
    geom_line() +
    labs(title = fcast.plot.title,
         subtitle = "ETS Model Forecasts",
         x = "", y = "Units") +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
    scale_color_tq() +
    scale_fill_tq() +
    facet_wrap(~ Region.x, scales = "free_y", ncol = 2) +
    theme_tq() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  #return.list <- list(model.params, data.plot.residuals, fcast.model.fit.tidy, data.plot.fcast)
  return.list <- list(model.params, fcast.model.fit.tidy)
  return(return.list)
}

##ARIMA Function
func.arima.mods <- function(nested.dataset, colName,
                          Exp.Variable,
                          d = 0,
                          D = 0,
                          Res.Plot.Title = "Insert.Plot.Title",
                          fcast.plot.title = "Insert Plot Title"){
  #test vars
  # nested.dataset <- TS.Nest.US.Sales.RollStock.Data
  # colName <- TS.Nest.US.Sales.RollStock.Data$FUEL.TBL.TS
  # Res.Plot.Title <- "Insert.Plot.Title"
  # fcast.plot.title <- "Insert Plot Title"
  #fit model
  model.fit <- nested.dataset %>%
    mutate(new.col.model.name = map(colName, auto.arima, d = d, D = D))
  
  #forecast model
  fcast.model.fit <- model.fit %>%
    mutate(fcast.model = map(new.col.model.name, forecast, h = 12))
  
  #model parameters
  #ARIMA
  model.params <- model.fit %>%
    mutate(tidy = map(new.col.model.name, sw_glance)) %>%
    unnest(tidy, .drop=TRUE) %>%
    mutate(Exp.Variable = rep(Exp.Variable)) %>%
    select(Region.x, model.desc, AIC, BIC, RMSE, MAPE, Exp.Variable)

  #get tidy model residuals
  augment.data <- model.fit %>%
    mutate(augment.var = map(new.col.model.name, 
                         sw_augment, 
                         timetk_idx = TRUE, 
                         rename_index = "Date")) %>%
    unnest(augment.var, .drop = TRUE)
  
  #plot model residuals 
  data.plot.residuals <- augment.data %>%
    ggplot(aes(x = Date, y = .resid, group = Region.x)) +
    geom_hline(yintercept = 0, color = "grey40") +
    geom_line(color = palette_light()[[2]]) +
    geom_smooth(method = "loess") +
    labs(title = Res.Plot.Title,
         subtitle = "ARIMA Model Residuals", x = "") +
    theme_tq() +
    facet_wrap(~ Region.x, scale = "free_y", ncol = 2) +
    scale_x_date(date_labels = "%Y")
  
  #get tidy forecast data
  fcast.model.fit.tidy <- fcast.model.fit %>%
    mutate(sweep = map(fcast.model, 
                       sw_sweep, 
                       fitted = TRUE,
                       timetk_idx = TRUE)) %>% 
    unnest(sweep)
  
  #plot fcast
  data.plot.fcast <- fcast.model.fit.tidy %>%
    ggplot(mapping = aes_string(x =  names(fcast.model.fit.tidy)[2], 
                      y = names(fcast.model.fit.tidy)[4], 
                      color = names(fcast.model.fit.tidy)[3], 
                      group = names(fcast.model.fit.tidy)[1])) + 
    geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
                fill = "#D5DBFF", color = NA, size = 0) +
    geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
                fill = "#596DD5", color = NA, size = 0, alpha = 0.8) +
    geom_line() +
    labs(title = fcast.plot.title,
         subtitle = "ARIMA Model Forecasts",
         x = "", y = "Units") +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
    scale_color_tq() +
    scale_fill_tq() +
    facet_wrap(~ Region.x, scales = "free_y", ncol = 2) +
    theme_tq() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  #return.list <- list(model.params, data.plot.residuals, fcast.model.fit.tidy, data.plot.fcast)
  return.list <- list(model.params, fcast.model.fit.tidy)
  return(return.list)
}
```


```{r load expense data function, echo = FALSE}
#check elapse time of function
# system.time(func.load.exp("Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Data/rolling.stock.focus/US.Rolling.Stock.Expense.csv"))

#load expense data
expense.data <- func.load.exp("Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Data/rolling.stock.focus/US.Rolling.Stock.Expense.csv")
```

```{r load sales data, echo = FALSE}
# system.time(func.load.sales("Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Data/US_Region_Division_Added_Only_NA_Item_Sales_chopdown_test a557ef9eb.csv"))

US.Sales.Data <- func.load.sales("Y:/Sharepoint Projects/Jason Marshall/R_Projects/OPEX_Forecasting/Data/US_Region_Division_Added_Only_NA_Item_Sales_chopdown_test a557ef9eb.csv")
```

```{r join datasets, echo = FALSE}
#system.time(func.join.datasets(US.Sales.Data, expense.data))
US.Sales.RollStock.Data <- func.join.datasets(US.Sales.Data, expense.data)
```

```{r nest data by Region, echo = FALSE}
#system.time(nest.data(US.Sales.RollStock.Data))
nested.dataset <- func.nest.data(US.Sales.RollStock.Data)
```

```{r nest data into TS objects}
ts.nested.dataset <- func.ts.nest.dataset(nested.dataset)

#Get first column of ts object
ts.nested.dataset %>%
  .$FUEL.TBL.TS %>%
  .[[1]] %>%
  .[,1]


ts.nested.dataset %>%
  .$FUEL.TBL.TS

lapply(unlist(ts.nested.dataset$FUEL.TBL.TS, recursive = FALSE), '[', "Total.Sales")
  
```

```{r PLOT EACH  fuel TS OBJECT, echo=FALSE}
# #plot fuel data vs sales
# for (i in 1:6) {
# region.name <- ts.nested.dataset$Region.x[[i]]
# ts.plot <- autoplot(ts.nested.dataset$FUEL.TBL.TS[[i]]) +
#   geom_smooth(method = 'loess') +
#   ggtitle(paste("Fuel", region.name, sep = ": ")) +
#   theme(legend.position="bottom")
# print(ts.plot)
# }
#ts.nested.dataset

map2(.x = ts.nested.dataset$FUEL.TBL.TS,
     .y = ts.nested.dataset$Region.x,
    .f = ~ autoplot(.x) + geom_smooth(method = 'loess') + 
      ggtitle(paste("Fuel", .y , sep = ": ")) + 
      theme(legend.position="bottom"))
```

```{r PLOT EACH RM Delivery Vehicle OBJECT, echo=FALSE}
#plot RM Field 
#for (i in 1:6){
# region.name <- ts.nested.dataset$Region.x[[i]]
# ts.plot <- autoplot(ts.nested.dataset$RM.DELIVERY.VEHIX.TBL.TS[[i]]) +
#   geom_smooth(method = 'loess') +
#   ggtitle(paste("Delivery Vehicle", region.name, sep = ": ")) +
#   theme(legend.position="bottom")
# print(ts.plot)
# }

map2(.x = ts.nested.dataset$RM.DELIVERY.VEHIX.TBL.TS ,
     .y = ts.nested.dataset$Region.x,
    .f = ~ autoplot(.x) + geom_smooth(method = 'loess') + 
      ggtitle(paste("Fuel", .y , sep = ": ")) + 
      theme(legend.position="bottom"))

```

```{r PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
#for (i in 1:6){
#region.name <- ts.nested.dataset$Region.x[[i]]
# ts.plot <- autoplot(ts.nested.dataset$RM.FIELD.EQUIP.TBL.TS[[i]]) + 
#   geom_smooth(method = 'loess') +
#   ggtitle(paste("RM Field Equip", region.name, sep = ": ")) +
#   theme(legend.position="bottom")
# print(ts.plot)
# }

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
  map2(.x = ts.nested.dataset$RM.FIELD.EQUIP.TBL.TS ,
     .y = ts.nested.dataset$Region.x,
    .f = ~ autoplot(.x) + geom_smooth(method = 'loess') + 
      ggtitle(paste("FIELD.EQUIP", .y , sep = ": ")) + 
      theme(legend.position="bottom"))
```

```{r PLOT EACH combo.plant.field, echo=FALSE}
#plot RM Field and plant equip vs sales
#for (i in 1:6){
# region.name <- ts.nested.dataset$Region.x[[i]]
# ts.plot <- autoplot(ts.nested.dataset$COMBO.PLANT.FIELD.TBL.TS[[i]]) +
#   geom_smooth(method = 'loess') +
#   ggtitle(paste("COMBO.PLANT.FIELD", region.name, sep = ": ")) +
#   theme(legend.position="bottom")
# print(ts.plot)
# }

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS

map2(.x = ts.nested.dataset$COMBO.PLANT.FIELD.TBL.TS ,
   .y = ts.nested.dataset$Region.x,
  .f = ~ autoplot(.x) + geom_smooth(method = 'loess') + 
    ggtitle(paste("PLANT.FIELD", .y , sep = ": ")) + 
    theme(legend.position="bottom"))



```

```{r PLOT EACH Rolling Stock OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
# for (i in 1:6){
# region.name <- ts.nested.dataset$Region.x[[i]]
# ts.plot <- autoplot(ts.nested.dataset$ROLL.STOCK.TOTAL.TBL.TS[[i]]) +
#   geom_smooth(method = 'loess') +
#   ggtitle(paste("Rolling Stock Total", region.name, sep = ": ")) +
#   theme(legend.position="bottom")
# print(ts.plot)
# }

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS

map2(.x = ts.nested.dataset$ROLL.STOCK.TOTAL.TBL.TS ,
   .y = ts.nested.dataset$Region.x,
  .f = ~ autoplot(.x) + geom_smooth(method = 'loess') + 
    ggtitle(paste("Rollstock Total", .y , sep = ": ")) + 
    theme(legend.position="bottom"))


```

```{r PLOT EACH total sales OBJECT, echo=FALSE}
#plot total sales
for (i in 1:6){
region.name <- ts.nested.dataset$Region.x[[i]]
ts.plot <- autoplot(ts.nested.dataset$TOTAL.SALES.TBL.TS [[i]]) +
  geom_smooth(method = 'loess') +
  ggtitle(paste("Net Sales Total", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

## ACF PACF Plots 
```{r ACF PLOT EACH RM Delivery Vehicle OBJECT, echo=FALSE}
#plot RM Field 
for (i in 1:6){
  region.name <- ts.nested.dataset$Region.x[[i]]
  ts.plot <- ggAcf(ts.nested.dataset$RM.DELIVERY.VEHIX.TBL.TS[[i]]) +
    ggtitle(paste("ACF Plot Delivery Vehicle", region.name, sep = ": ")) +
    theme(legend.position="bottom")
  
  ts.plot.2 <- ggPacf(ts.nested.dataset$RM.DELIVERY.VEHIX.TBL.TS[[i]]) + 
    ggtitle(paste("PACF Plot Delivery Vehicle", region.name, sep = ": ")) +
    theme(legend.position="bottom")
  print(ts.plot)
  print(ts.plot.2)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```
##Commentary 
#Central Cornbelt: Sig autocorrelation at lag 1, light seasonal autocorr at lag 12
#Eastern: Sig autocorr at lag 1, light seasonal autocorr at lag 12
#ECB: Sig autocorr at lag 1, sig seasonal autocorr at lag 12
#South: Sig autocorr at lag 1, no sig seasonal autocorr at lag 12, sig negative auto.corr at lag 18
#West: Sig autocorr at lag 1, no sig autocorr at lag 12, light neg autocorr at 16/18.
#Western.Cornbelt: Sig autocorr at lag 1, no sig autocorr at lag 12. sig neg autocorr at lag 15.

```{r ACF PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- ts.nested.dataset$Region.x[[i]]
ts.plot <- ggAcf(ts.nested.dataset$RM.FIELD.EQUIP.TBL.TS[[i]]) + 
  ggtitle(paste("ACF Plot RM Field Equip", region.name, sep = ": ")) +
  theme(legend.position="bottom")
ts.plot.2 <- ggPacf(ts.nested.dataset$RM.FIELD.EQUIP.TBL.TS[[i]]) + 
    ggtitle(paste("PACF Plot RM Field Equip", region.name, sep = ": ")) +
    theme(legend.position="bottom")
  print(ts.plot)
  print(ts.plot.2)
print(ts.plot)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

##Commentary
#CCB: Sig autocorr at lag 1, no seasonal autocorr
#Eastern: sig autocorr at lag 1, no seasonal autocorr
#ECB: Sig autocorr at lag 1, light seasonal autocorr
#South: Sig autocorr at lag 1, marginal seasonal autocorr
#West: Sig autocorr at lag 1, no seasonal autocorr
#WCB: Sig autocorr at lag 1, Sig seasonal autocorr

```{r ACF PLOT EACH RM Field Equip Vehicle OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
region.name <- ts.nested.dataset$Region.x[[i]]
ts.plot <- ggAcf(ts.nested.dataset$COMBO.PLANT.FIELD.TBL.TS[[i]]) + 
  ggtitle(paste("ACF Plot COMBO PLANT and FIELD", region.name, sep = ": ")) +
  theme(legend.position="bottom")
ts.plot.2 <- ggPacf(ts.nested.dataset$COMBO.PLANT.FIELD.TBL.TS [[i]]) + 
  ggtitle(paste("PACF Plot COMBO PLANT and FIELD", region.name, sep = ": ")) +
  theme(legend.position="bottom")
print(ts.plot)
print(ts.plot.2)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

##Commentary
#CCB: moderate autocorr at lag 1, sig seasonal autocorr
#Eastern: sig autocorr at lag 1, sig seasonal autocorr
#ECB: Sig autocorr at lag 1, Sig seasonal autocorr
#South: Sig autocorr at lag 1, SIG seasonal autocorr
#West: Sig autocorr at lag 1, SIG seasonal autocorr
#WCB: Sig autocorr at lag 1, Sig seasonal autocorr

```{r ACF PLOT EACH Rolling Stock OBJECT, echo=FALSE}
#plot RM Field and plant equip vs sales
for (i in 1:6){
  region.name <- ts.nested.dataset$Region.x[[i]]
  ts.plot <- ggAcf(ts.nested.dataset$ROLL.STOCK.TOTAL.TBL.TS[[i]]) + 
    ggtitle(paste("ACF Plot Rolling Stock Total", region.name, sep = ": ")) +
    theme(legend.position="bottom")
  ts.plot.2 <- ggPacf(ts.nested.dataset$ROLL.STOCK.TOTAL.TBL.TS[[i]]) + 
    ggtitle(paste("PACF Plot Rolling Stock Total", region.name, sep = ": ")) +
    theme(legend.position="bottom")
  print(ts.plot)
  print(ts.plot.2)
}

#TS.Nest.US.Sales.RollStock.Data$RM.PLANT.FIELD.TBL.TS
```

##Commentary
#CCB: moderate autocorr at lag 1, sig seasonal autocorr @ lag 12
#Eastern: sig autocorr at lag 1, sig seasonal autocorr @ lag 12
#ECB: Sig autocorr at lag 1, Sig seasonal autocorr @ lag 12
#South: Sig autocorr at lag 1, SIG seasonal autocorr @ lag 12
#West: Sig autocorr at lag 1, SIG seasonal autocorr @ lag 12
#WCB: Sig autocorr at lag 1, Sig seasonal autocorr @ lag 12

```{r ACF PLOT EACH  sales TS OBJECT, echo=FALSE}
#plot fuel data vs sales
for (i in 1:6) {
  region.name <- ts.nested.dataset$Region.x[[i]]
  ts.plot <- ggAcf(ts.nested.dataset$TOTAL.SALES.TBL.TS[[i]]) + 
    ggtitle(paste("ACF Plot Net.Sales", region.name, sep = ": ")) +
    theme(legend.position="bottom")
  ts.plot.2 <- ggPacf(ts.nested.dataset$TOTAL.SALES.TBL.TS[[i]]) + 
      ggtitle(paste("PACF Plot Net.Sales", region.name, sep = ": ")) +
      theme(legend.position="bottom")
    print(ts.plot)
    print(ts.plot.2)
  
}
```


```{r ETS Model Metrics }
# function(nested.dataset, colName,
#                           Exp.Variable,
#                           Res.Plot.Title = "Insert.Plot.Title",
#                           fcast.plot.title = "Insert Plot Title"
#colnames(ts.nested.dataset)
#func.ets.mods()
ets.model.fuel <- func.ets.mods(nested.dataset = ts.nested.dataset, 
                                colName = ts.nested.dataset$FUEL.TBL.TS,
                                Exp.Variable = "FUEL.Exp")
#ets.model.fuel

ets.model.delivery <- func.ets.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Delivery",
                                colName = ts.nested.dataset$RM.DELIVERY.VEHIX.TBL.TS)
#ets.model.delivery

ets.model.field <- func.ets.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Field",
                                colName = ts.nested.dataset$RM.FIELD.EQUIP.TBL.TS)
#ets.model.field

ets.model.combo <- func.ets.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Delivery/Field",
                                colName = ts.nested.dataset$COMBO.PLANT.FIELD.TBL.TS)
#ets.model.combo

ets.model.rolls.stock <- func.ets.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Roll.Stock.Total",
                                colName = ts.nested.dataset$ROLL.STOCK.TOTAL.TBL.TS)
#ets.model.rolls.stock[[1]]

ets.metrics <- rbind(ets.model.fuel[[1]], ets.model.delivery[[1]], ets.model.field[[1]],
                     ets.model.combo[[1]], ets.model.rolls.stock[[1]])
ets.metrics

ets.model.fuel[[2]]

# ets.fcast <- rbind(ets.model.fuel[[2]], ets.model.delivery[[2]], ets.model.field[[2]],
#                      ets.model.combo[[2]], ets.model.rolls.stock[[2]])
ets.metrics
```

```{r ARIMA Model Metrics }
ARIMA.model.fuel <- func.arima.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "FUEL.Exp",
                                colName = ts.nested.dataset$FUEL.TBL.TS, d = 0, D = 1)
#ARIMA.model.fuel

ARIMA.model.delivery <- func.arima.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Delivery",
                                colName = ts.nested.dataset$RM.DELIVERY.VEHIX.TBL.TS)
#ARIMA.model.delivery

ARIMA.model.field <- func.arima.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Field",
                                colName = ts.nested.dataset$RM.FIELD.EQUIP.TBL.TS)
#ARIMA.model.field

ARIMA.model.combo <- func.arima.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Delivery/Field",
                                colName = ts.nested.dataset$COMBO.PLANT.FIELD.TBL.TS)
#ARIMA.model.combo

ARIMA.model.rolls.stock <- func.arima.mods(nested.dataset = ts.nested.dataset, Exp.Variable = "Roll.Stock.Total",
                                colName = ts.nested.dataset$ROLL.STOCK.TOTAL.TBL.TS)
#ARIMA.model.rolls.stock[[1]]

ARIMA.metrics <- rbind(ARIMA.model.fuel[[1]], ARIMA.model.delivery[[1]], ARIMA.model.field[[1]],
                     ARIMA.model.combo[[1]], ARIMA.model.rolls.stock[[1]])
ARIMA.metrics

```


```{r fit model to MTS object}

auto.arima.xreg <- function(ts.nested.list = ts.nested.dataset$FUEL.TBL.TS,
                            xreg.nested.list = ts.nested.dataset$TOTAL.SALES.TBL.TS){
  fit <- auto.arima(ts.nested.dataset$FUEL.TBL.TS, xreg = ts.nested.dataset$TOTAL.SALES.TBL.TS)
  return(fit)
}



mod <- list()
for (i in 1:6){
mod <- lapply(ts.nested.dataset$FUEL.TBL.TS, function(x) auto.arima(ts.nested.dataset$FUEL.TBL.TS[[i]][1], 
                                                        xreg = ts.nested.dataset$FUEL.TBL.TS[[i]][2]))
}

mod
ts.nested.dataset$FUEL.TBL.TS
ts.nested.dataset$FUEL.TBL.TS[[1]][,1]
ts.nested.dataset$FUEL.TBL.TS[[1]][,2]
mod


ts.nested.dataset$FUEL.TBL.TS


arima.list <- list()


func_ARIMA_XREG <- function(dataset_and_Index, Index){
for (i in 1:6)
  
  arima_fit <- auto.arima(y = dataset %>%
                            .$FUEL.TBL.TS %>%
                            .[[1]] %>%
                            .[,1],
                  xreg = dataset %>%
                            .$FUEL.TBL.TS %>%
                            .[[1]] %>%
                            .[,2])
  #ts.nested.dataset$ARIMAXREG <- x
  return(arima_fit)
}


ts.nested.dataset <- ts.nested.dataset %>% 
  ts.nested.dataset[,10] %>% 
  mutate(test = map(., func_ARIMA_XREG))


test[[1]]

ts.nested.dataset[,c(10)][[2]][1]
arima.list
```






















